### 2017-08-29 README.Rmd
pkg clean up

---
output: github_document
bibliography: refs.bib
---

@@

* The _average treatment effect_ (ATE):
  $$ \Psi_{ATE} = E[E[Y_j \mid A = 1, W_{-j}] - E[Y_j \mid A = 0, W_{-j}]],$$
  where $j$ indexes a target CpG site of interest and $-j$ gives all CpG sites
  in the same neighborhood as the target site except the target site itself
  (i.e., the neighboring sites).

* The _relative risk_ (RR), where
  $$ \dots,$$
  where...

@@

* A _nonparametric variable importance measure_ (NPVI) [@chambaz2012estimation].

@@

&copy; 2017 [Nima S. Hejazi](http://nimahejazi.org), [Alan E.
Hubbard](http://sph.berkeley.edu/alan-hubbard), [Mark J. van der
Laan](https://www.stat.berkeley.edu/~laan/)

@@

## References

>>>>

---
output: rmarkdown::github_document
bibliography: README-refs.bib
---

@@

* The _average treatment effect_ (ATE): The effect of a binary exposure or
  treatment on the observed methylation at a target CpG site is estimated,
  controlling for the observed methylation at all other CpG sites in the same
  neighborhood as the target site, based on an additive form. In particular, the
  parameter estimate represents the __additive difference__ in methylation that
  would have been observed at the target site had all observations received the
  treatment versus the scenario in which none received the treatment.

* The _relative risk_ (RR): The effect of a binary exposure or treatment on the
  observed methylation at a target CpG site is estimated, controlling for the
  observed methylation at all other CpG sites in the same neighborhood as the
  target site, based on an geometric form. In particular, the parameter estimate
  represents the __multiplicative difference__ in methylation that would have
  been observed at the target site had all observations received the treatment
  versus the scenario in which none received the treatment.

@@

* A _nonparametric variable importance measure_ (NPVI) [@chambaz2012estimation]:
  The effect of continous-valued exposure or treatment (the observed methylation
  at a target CpG site) on an outcome of interest is estimated, controlling for
  the observed methylation at all other CpG sites in the same neighborhood as
  the target (treatment) site, based on a parameter that compares values of the
  treatment against a reference value taken to be the null. In particular, the
  implementation provided is designed to assess the effect of differential
  methylation at the target CpG site on a (typically) phenotype-level outcome
  of interest (e.g., survival), in effect providing an nonparametric evaluation
  of the impact of methylation at the target site on said outcome.

_In all cases, an estimator of the target parameter is constructed via targeted
minimum loss-based estimation._

@@

&copy; 2017 [Nima S. Hejazi](http://nimahejazi.org)

@@
